Paper 1

### 2022-05-27 scripts/Paper 1.Rmd
u

```{r setup, include=FALSE}
library(dplyr)
library(data.table)
library(janitor)
library(plotly)
library(plyr)
library(knitr)
library(tidyverse)
#library(devtools)
library(openair)
library(tidyr)
library(naniar)
library(forecast)

@@

```{r create rainfall summary}
rainfall.summary <- rainfall %>% ddply(c("Year", "Site", "season"), summarise,
                                       seasonal.sum = sum(Precip, na.rm = TRUE))
rainfall.summary %>% 
  ggplot(., aes(x = season, y = seasonal.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()

>>>>

```{r setup, include=FALSE}
library(dplyr)
library(data.table)
library(janitor)
library(plotly)
library(plyr)
library(knitr)
library(tidyverse)
#library(devtools)
library(openair)
library(tidyr)
library(naniar)
library(forecast)
library(kableExtra)

@@

```{r create rainfall summary}
rainfall.summary <- rainfall %>% ddply(c("Year", "Site", "season"), summarise,
                                       seasonal.sum = sum(Precip, na.rm = TRUE))

rainfall.summary %>% kbl() %>% kable_styling()

rainfall.summary %>% 
  ggplot(., aes(x = season, y = seasonal.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()
